Sound Automated Synthesis of Digital Controllers

### 2016-10-11 paper/paper.tex
Minor changes

\begin{mylemma}
\label{lemma:variance}
In particular, \cite{widrow1956} models the quantisation noise as a gaussian
model in which the second moment (variance) of the probability density
function (PDF) of the quantisation noise is given by
%
\begin{equation}
\label{eq:variancelemma}
\sigma_{Q}^{2}=\frac{q^{2}}{12},
\end{equation}
where $q$ is the step size of quantizer. (Proof is on \cite{widrow1956})
\end{mylemma}

\begin{mylemma}
\label{lemma:boundednoise}
The z-transform of the quantisation noise $\nu(z)=\mathcal{Z}\left\lbrace\nu(k)\right\rbrace$ in figure~\ref{fig:digsystem1} may be calculated through the power spectral density of $\nu(k)$, thus:
\begin{equation}
\nu(z)= \sigma_{Q}^{2}.
\end{equation}
\end{mylemma}

@@

By definition~\cite{poularikas2000transforms}, the power spectral density of  $nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
\begin{equation}
\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2}.
\end{equation}
\end{proof}

>>>>

\begin{mylemma}
\label{lemma:variance}
In particular, Widrow \cite{widrow1956} models the quantisation noise as a gaussian
model in which the second moment (variance) of the probability density
function (PDF) of the quantisation noise is given by
%
\begin{equation}
\label{eq:variancelemma}
\sigma_{Q}^{2}=\frac{q^{2}}{12},
\end{equation}
where $q$ is the step size of quantizer. (Proof is on \cite{widrow1956})
\end{mylemma}

\begin{mylemma}
\label{lemma:boundednoise}
The power spectral density of the quantisation noise (supposed white) $S_{\nu}(z)$ is bounded and may be computed through the z-transform of autocorrelation function of $\nu(k)$, thus:
\begin{equation}
S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
\end{equation}
\end{mylemma}

@@

By definition~\cite{poularikas2000transforms}, the power spectral density of  $nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
\begin{equation}
\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
\end{equation}
considering the Lemma~\ref{lemma:variance}:
\begin{equation}
\nu(z)=  \frac{q^{2}}{12}.
\end{equation}
\end{proof}

Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
